Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-12 manuscript/manuscript.tex
Update grid search text

@@

We aim to find a combination of the $D$ and $\delta$ that produces a numerical error
lower than the 0.1\% threshold while minimizing computation time.
We use a grid search method and compute the numerical error for every ($D$, $\delta$)
pair belonging to a grid on the $D$-$\delta$ space (Fig. \ref{fig:grid-search}).
Because this is a time consuming computation, we limit the analysis to a shell of 35 km
thickness and $b = 1\ \text{km}$ (Eq. \ref{eq:density-exp}), which yields a
sharp density variation within the shell.
For optimum algorithm performance, we search for the smallest possible value of $D$ and
the highest possible value of $\delta$.

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$), the vertical component of its gradient ($g_z$), and the
$g_{zz}$ component of the Marussi tensor.
The results are shown in Fig. \ref{fig:grid-search}, in which points inside the dotted
lines are the ones that present a numerical error lower than the 0.1\% threshold.
Also shown in Fig. \ref{fig:grid-search} are the $D$ values determined for the linear
density function in the previous section ($D_\text{linear}$).
The values of $D_\text{linear}$ are within the 0.1\% threshold and are the optimum
values of $D$ for $V$ and $g_z$.
The results for $g_{zz}$ are in agreement with those obtained for the linear density
function in the case of a thick shell (Fig. \ref{fig:D-linear}).
Thus, we also choose the conservative value of $D=8$ as the optimum value for $g_{zz}$.
These results indicate that the values of $D_\text{linear}$ can be safely extrapolated
to the exponential case.

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/exponential-densities.pdf}
\caption{
    Exponential density functions assigned to each spherical shell in the $D$ and
    $\delta$ ratios determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-exp}.
}
\label{fig:exp-densities}
\end{figure}

@@

We aim to find a combination of the $D$ and $\delta$ that produces a numerical error
lower than the 0.1\% threshold while minimizing computation time.
We use a grid search method and compute the numerical error for every ($D$, $\delta$)
pair belonging to a grid on the $D$-$\delta$ space (Fig.~\ref{fig:grid-search}).
For optimum algorithm performance, we search for the ($D$, $\delta$) pair that minimize
the number of splittings while keeping a numerical error under the 0.1\% threshold,
i.e.~the smallest possible value of $D$ and the highest possible value of $\delta$.

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the vertical component of its gradient ($g_z$) on the
computation grids detailed in Table~\ref{tab:grids} and using shell models with the same
thicknesses as the linear density case.
Because this is a time consuming computation, we limit the analysis only to the second
collection of tesseroids in Table~\ref{tab:tess-collections}.
For the sake of brevity, we compute the maximum differences between the results
involving each computation grid, shell thickness and value of the $b$ factor.
The results are shown in Fig.~\ref{fig:grid-search}, in which points inside the dotted
lines are the ones that present a numerical error lower than the 0.1\% threshold.
Also shown in Fig. \ref{fig:grid-search} are the $D$ values determined for the linear
density function in the previous section ($D_\text{linear}$).
The values of $D_\text{linear}$ are within the 0.1\% threshold and are the optimum
values of $D$ for $V$ and $g_z$.
These results indicate that the values of $D_\text{linear}$ can be safely extrapolated
to the exponential case.

The two dimensional adaptive discretization and the density-based algorithms are
independent of each other: the first one splits the tesseroid only in the latitudinal
and longitudinal directions, while the latter only does it in the radial direction.
This leads to the fact that the value of $\delta$ needed to limit the numerical error
due to the density variation is independent of the value of $D$.
